\begin{thebibliography}{50}
 \bibitem{esp1} D. P. Woodruff, W. A. Royer, N. V. Smith (1986), \emph{Physical Review B} {\bf 34}, 2.
 \bibitem{esp2} K. Giesen, F. Hage, F. J. Himpsel, H. J. Riess, W. Steinmann (1986), \emph{Physical Review B} {\bf 33}, 8.
  \bibitem{esp3} M. Ortuno, P. M. Echenique (1986), \emph{Physical Review B} {\bf 34}, 8.
  \bibitem{A-B} J. A. Appelbaum, E. I. Blount (1973), \emph{Physical Review B} {\bf 8}, 483.
 \bibitem{Art:PG} J. B. ~Pendry, S. J. Gurman (1974), \emph{Surface Science } {\bf 49}, 87-105.   
 \bibitem{Art:Griffiths} David J.~Griffiths (2005), \emph{Introduzione alla Meccanica Quantistica}, Ambrosiana.
\bibitem{Acciarri} N. W. Ashcroft, N. D. Mermin (1976), \emph{Solid State Physics}, Holt, Rinehart, Winston.
	\bibitem {2bande} P. M. Echenique, J. M. Pitarke, E. V. Chulkov, V. M. Silkin (2008), \emph{Journal of electron spectroscopy and related phenomena} {\bf 126}, 163-175.
\bibitem{Art:Chulkov} E. V. ~Chulkov, V. M. Silkin, P. M. Echenique (1999), \emph{Surface Science} {\bf 437}, 330-352.
 \bibitem{Cohen:quantum1} C.~Cohen-Tannoudji, B.~Diu, F.Laloe (1973), \emph{Quantum Mechanics}, Vol.~1, Wiley-VCH.
\bibitem{bucatri}  J. H. Davies (1998), \emph{The Physiscs of Low Dimensional Semiconductors-An Introduction}, Cambridge University Press.
   \bibitem{Cohen:quantum2} C.~Cohen-Tannoudji, B.~Diu, F.Laloe (1973), \emph{Quantum Mechanics}, Vol.~2, Wiley-VCH.
 \bibitem{Art:EP} P. M. ~Echenique, J. B. Pendry (1977), \emph{Solid State Physics} {\bf 11}, 2065.
 \bibitem{Art:Smith} N. V. ~Smith (1985), \emph{Physical Review B} {\bf 32}, 6.
   \bibitem {} G.Butti (2005) \emph{PhD Thesis: Surface specific electronic structure on extended substrates}.

\end{thebibliography}